Letter from ANU

### 2025-07-29 cover_letter/letter.qmd
Add a conflict of interest statement and a original work statement in the cover letter
Add co-author info and sign

---
format: quarto-anu-letter-pdf
author:
  - name: "\u200B" # I need to sign this
    position: Postdoctoral Research Fellow 
    affiliation:
      - name: Australian National University
        department: Research School of Finance, Actuarial Studies and Statistics
        address: "26C Kingsley Street"  
        city: Canberra
        country: Australia
        postal-code: 2600
address:
  - Editors,
  - Journal of Computational and Graphical Statistics
title: Letter from ANU
opening: "Dear Prof. Chen and Prof. Sangalli,"
closing: "Sincerely,"
keep-tex: true
---

@@

@@

@@

>>>>

---
format: quarto-anu-letter-pdf
author:
  - name: "\u200B" # I need to sign this
    position: Postdoctoral Research Fellow 
    affiliation:
      - name: Australian National University
        department: Research School of Finance, Actuarial Studies and Statistics
        address: "26C Kingsley Street"  
        city: Canberra
        country: Australia
        postal-code: 2600
address:
  - Editors,
  - Journal of Computational and Graphical Statistics
title: Letter from ANU
opening: "Dear Prof. Chen and Prof. Sangalli,"
closing: ""
keep-tex: true
---

@@

We confirm that this work is original and has not been published elsewhere, nor is it currently under consideration for publication elsewhere.

@@

We have no conflict of interest to disclose.

Please address all corresponding concerning this manuscript to me at patrick.li@anu.edu.au.

@@

Sincerely,

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

Dr. Weihao Li\newline
Postdoctoral Research Fellow, Research School of Finance, Actuarial Studies and Statistics\newline
Australian National University

Co-author

Prof. Dianne Cook\newline
Professor, Department of Econometrics and Business Statistics\newline
Monash University

Dr. Emi Tanaka\newline
Senior Lecturer, Research School of Finance, Actuarial Studies and Statistics\newline
Australian National University

Dr. Susan VanderPlas\newline
Associate Professor, Department of Statistics\newline
University of Nebraska

Dr. Klaus Ackermann\newline
Associate Professor, Department of Econometrics and Business Statistics\newline
Monash University

### 2025-07-29 cover_letter/letter.tex
Recompile
Add co-author info and sign

\closing{Sincerely,}
\vfill
\end{letter}
\end{document}

>>>>

Sincerely,

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

Dr.~Weihao Li\newline Postdoctoral Research Fellow, Research School of
Finance, Actuarial Studies and Statistics\newline Australian National
University

Co-author

Prof.~Dianne Cook\newline Professor, Department of Econometrics and
Business Statistics\newline Monash University

Dr.~Emi Tanaka\newline Senior Lecturer, Research School of Finance,
Actuarial Studies and Statistics\newline Australian National University

Dr.~Susan VanderPlas\newline Associate Professor, Department of
Statistics\newline University of Nebraska

Dr.~Klaus Ackermann\newline Associate Professor, Department of
Econometrics and Business Statistics\newline Monash University

\vfill
\end{letter}
\end{document}
